%
% ----- copyright and title pages
%
\Title{Semantic Knowledge Management Framework\\for Learning Organizations}
\Author{Brendan Sweeney}
\Year{2015}
\Program{Cyber Security Engineering}

\Chair{Brent Lagesse}{Assistant Professor}{School of STEM Computing and Software Systems Division}
\Signature{Mark Kochanski}
\Signature{Marc Dupuis}
\Signature{Joe McCarthy}

\copyrightpage

\Degreetext{A report\\
            submitted in partial fulfillment of the\\
            requirements of the degree of}
\Degree{Master of Science in Cyber Security Engineering}
\textofCommittee{Project Committee:}

\titlepage

\setcounter{page}{-1}
\abstract{Knowledge management systems (KMS) allow organizations to capture, refine, and redistribute knowledge between members with minimal effort. Learning organizations, in particular, can benefit from such systems thanks to the capability these systems provide to transfer knowledge from individuals into a repository that is readily accessible to the entire group. While a complete knowledge management system incorporates a multitude of tools and resources, a major cornerstone of any modern KMS is a digital datastore in which information can be collected and correlated. In this project, Semantic Knowledge Management Framework, the author uses Semantic Web technologies to create a flexible foundation for the datastore component of a knowledge management system. This report begins with a brief comparison between relational database systems and graph-based information systems, including the author's reasons for choosing a graph-based approach built on RDF. Some similar applications are examined, both using relational databases and using Semantic Web frameworks. Next, some of the design decisions are discussed, along with the particular challenges of adapting programming objects to a dynamic RDF model and preparing SPARQL statements without a predefined schema. The project is demonstrated for use by a hypothetical computer security incident response team to track and manage assets, patches, policies, and team members. Finally, future goals and directions for the project are proposed.}

%
% ----- contents, etc.
%
\tableofcontents
\listoffigures
%\listoftables

%
% ----- glossary
%
\chapter*{Glossary}      % starred form omits the `chapter x'
\addcontentsline{toc}{chapter}{Glossary}
\thispagestyle{plain}

\begin{glossary}

\item[knowledge management] \colorbox{yellow}{The practice of} collecting, correlating, collating, and refining information so that it may be readily disseminated throughout an organization for members to act upon it.

\item[object] \colorbox{yellow}{In RDF triples,} the portion of the statement that provides the value that describes the subject.

\item[ORM] \colorbox{yellow}{Object-RDF Model.} Analogous to the object-relational model for relational databases, a description of how data modeled in the triplestore maps to the form and behavior of programming objects in running code.

\item[OWL] Web Ontology Language. A massive extension of RDF that includes finer classifications than RDFS and allows for logical inferences.

\item[predicate] \colorbox{yellow}{In RDF triples,} the portion of the statement that provides the property of the subject that is being described.

\item[RDF] Resource Description Framework. A cornerstone of the Semantic Web, RDF allows for uniquely identifiable (through URIs) resources to be describes in terms of triples which form a connected graph of semantically rich information.

\item[RDFS] \colorbox{yellow}{Resource Description Framework} Schema. An extension to RDF that provides additional pre-defined relationship types that can be used to describe resources.

\item[Semantic Web] \colorbox{yellow}{A machine-readable} representation of information on the World Wide Web that relates elements through semantic meaning.

\item[SKMF] Semantic Knowledge Management Framework; the software project that is discussed in this paper.

\item[SPARQL] SPARQL Protocol and RDF Query Language. Used to manipulate data stored in the RDF format.

\item[SPARQL endpoint] SPARQL Protocol and RDF Query Language. Used to manipulate data stored in the RDF format.

\item[subject] \colorbox{yellow}{In RDF triples,} the portion of the statement that identifies the resource that is being described.

\item[triple] \colorbox{yellow}{In RDF, a} three-part statement consisting of subject, predicate, and object. The subject is the resource being described, the predicate is a property of that resource, and the object is the value that applies to the given property of the given resource.

\item[triplestore] \colorbox{yellow}{A datastore that} is optimized for storage and retrieval of RDF triples.

\item[URI] \colorbox{yellow}{Uniform Resource Identifier.} In RDF, this is used to unambiguously identify a resource (subject or object) and a property (predicate).
 
\end{glossary}
 
%
% ----- acknowledgments
%
%\acknowledgments{% \vskip2pc
%  % {\narrower\noindent
%  The author wishes to express sincere appreciation to
%  University of Washington, where he has had the opportunity
%  to work with .
%  % \par}
%}

%
% ----- dedication
%
\dedication{\begin{center}in memory of my father, Dr. Frank Sweeney\end{center}}

%
% end of the preliminary pages
